---
title: "FO2D Group: 30"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: flatly
---

```{r setup, include=FALSE}
library(flexdashboard)
```

Overview
======================================================================

Sidebar {.sidebar}
-----------------------------------------------------------------------


### *Abstract*



Column
-----------------------------------------------------------------------

### **Central Graph = Main findings**

```{r}

```


```{r}
```

Column {data-width=350}
-----------------------------------------------------------------------

### Colected / Used data as playable playlist (Test)

```{r}
```


### Audio Features Explenation

```{r}
```
Feature | Explanation
------------ | -------------
Valence | A measure from 0 to 1 describing the musical positiveness conveyed by a track. Tracks with high valence sound more positive (e.g. happy, cheerful), while tracks with low valence sound more negative (e.g. sad, angry).
Energy | Energy is a measure from 0 to 1 and represents a perceptual measure of intensity and activity. Typically, energetic tracks feel fast, loud, and noisy. 
Danceability | Danceability describes how suitable a track is for dancing based on a combination of musical elements (such as tempo), measured from 0 to 1.
Instrumentalness | Predicts whether a track contains no vocals. “Ooh” and “aah” sounds are treated as instrumental in this context. The closer to 1, since it is measured from 0 to 1, the more instrumental the song is.
Acousticness | A confidence measure from 0 to 1 of whether the track is acoustic. 1 represents acousticness, and means there are no electric sounds involved.
Speechiness | Speechiness detects the presence of spoken words in a track. Measured from 0 to 1, the more speech, the closer to 1.
Liveness | Detects the presence of an audience in the recording. Higher liveness values represent an increased probability that the track was performed live, measured from 0 to 1.
Loudness | The overall loudness of a track in decibels (dB). Values typical range between -60 and 0 db (represented on a scale from 0 - 1)
Tempo | The overall estimated tempo of a track in beats per minute (BPM). Tempo is the speed or pace of a given piece and derives directly from the average beat duration.

Background {data-orientation=rows}
=====================================================================
Column
---------------------------------------------------------------------
### Introduction

- Contextualizing RQ (still have to formulate it precisely)

### Methodlogy

- Data Collection = Survey to collect songs based on a criteria (we have to fidure out what)
- Music Infromation Retrieval using Rstudio, Python and the Spoitfy API

Column
---------------------------------------------------------------------
### Survey Results

Maybe group participants by demographic and display graphs per demographic or a different criteria??


Discussion
=====================================================================

Column
---------------------------------------------------------------------
### Discussion


Column {.tabset}
---------------------------------------------------------------------
### Final Results

### Raw Data

### References